method

### 2022-06-03 06_Paper/ER-ED/method.Rmd
added description of linear model for FlexER

The association between flexible ER and SVs of ER strategies (H7b) will be investigated with a linear regression using the individual $intercept$ (i.e., the extent to which an invididual considers any of the ER strategies useful) and $slope$ (i.e., the extent to which one strategy is preferred over others, indicating less flexibility) of each participants' SVs to predict their FlexER score.
To estimate individual $intercepts$ and $slopes$, SVs will first be sorted by magnitude in descending order.
Values will be fitted in a linear model to estimate individual $intercepts$ and $slopes$.

>>>>

The association between flexible ER and SVs of ER strategies (H7b) will be investigated with a linear regression using the individual $intercept$ and $slope$ of each participants' SVs to predict their FlexER score.
To this end, for each participant, SVs will be sorted by magnitude in descending order and entered as dependent variable in a linear model, with strategy (centered, i.e., -1, 0, 1) as independent variable.
The resulting $intercept$ informs about the extent to which an individual considers any or all of the ER strategies as useful for regulation their emotion, while the $slope$ informs about the flexibility in the use of emotion regulation strategies. 
The individual intercepts and slopes will then be entered as predictors in a regression model with the FlexER score as dependent variable. 
A positive association with the predictor $intercept$ would indicate that overall higher SVs attached to ER strategies predicts higher scores on the FlexER scale. 
A positive association with the predictor $slope$ would indicate that less negative slopes, i.e., a smaller preference for a given ER strategy, would be associated with a higher score of the FlexER scale.
